Slides and posters can be found on my \href{https://theoguyard.github.io/talks}{website}.

\begin{etaremune}
    \item December 9th, 2024, ``Solving L0-norm problems via mixed-integer optimization'', \textit{IMAG team seminar}, Montpellier, France.
    \item November 27th, 2024, ``Branch-and-Bound algorithms for L0-regularized problems'', \textit{PhD Defense}, Rennes, France.
    \item September 16th, 2024, ``Toward stronger relaxations for L0-regularized problems'', \textit{GdR IASIS Workshop}, Institut Henri Poincaré, France.
    \item July 24th, 2024, ``A new Branch-and-Bound pruning framework for L0-regularized problems'', \textit{ICML}, Vienna, Austria.
    \item March 28th, 2024, ``A generic Branch-and-Bound for L0-penalized problems'', \textit{SMAI-MODE days}, Lyon, France.
    \item March 28th, 2024, ``Screen-and-Relax for sparse support identification'', \textit{SMAI-MODE days}, Lyon, France.
    \item March 18th, 2024, ``Discrete optimization methods for L0-norm problems'', \textit{Journées Doctorants en Statistiques}, Rennes, France.
    \item March 7th, 2024, ``Mixed-integer optimization methods for sparse problems'', \textit{LS2N seminar}, Nantes, France.
    \item November 29th, 2023, ``Screen \& Relax for sparse support identification'', \textit{PGMO days}, Paris-Saclay, France.
    \item November 29th, 2023, ``Safe peeling for L0-penalized problems'', \textit{PGMO days}, Paris-Saclay, France.
    \item October 19th, 2023, ``Solving L0-norm problems via mixed-integer optimization'', \textit{INRIA EDGE team seminar}, Bordeaux, France.
    \item October 10th, 2023, ``Solving L0-norm problems via mixed-integer optimization'', \textit{INRIA SODA and MIND team seminar}, Paris-Saclay, France.
    \item September 9th, 2023, ``Peeling for L0-regularized least-squares'', \textit{EUSIPCO}, Helsinki, Finland.
    \item August 30th, 2023, ``Peeling for L0-regularized least-squares'', \textit{GRETSI}, Grenoble, France.
    \item May 2nd, 2023, ``Unifying Branch-and-Bound approaches to solve L0-penalized problems'', \textit{SIAM Conference on Optimization}, Seattle, USA.
    \item February 21st, 2023, ``An efficient solver for L0-penalized sparse problems'', \textit{ROADEF}, Rennes, France.
    \item February 17th, 2023, ``The latest report from the CNRS ethics committee: Integrating environmental issues into the conduct of research'', \textit{IRMAR Science and Ethic seminar}, Rennes, France.
    \item November 30th, 2022, ``Discrete optimization methods for L0-penalized sparse problems'', \textit{PGMO days}, Paris-Saclay, France.
    \item September 30th, 2022, ``Resilience in signal processing and AI'', \textit{IRMAR Science and Ethic seminar}, Rennes, France.
    \item September 8th, 2022, ``Node-screening pour le problème des moindres carrés avec pénalité L0'', \textit{GRETSI}, Nancy, France.
    \item September 8th, 2022, ``Accélérer la résolution de l’Elastic-Net par identification du support de la solution'', \textit{GRETSI}, Nancy, France.
    \item June 1st, 2022, ``Node-screening tests for the L0-penalized least-squares problem'', \textit{SMAI-MODE days}, Limoges, France.
    \item May 8th, 2022, ``Node-screening tests for the L0-penalized least-squares problem'', \textit{ICASSP}, Singapore.
    \item May 8th, 2022, ``Screen \& Relax: Accelerating the resolution of Elastic-Net by safe identification of the solution support'', \textit{ICASSP}, Singapore.
\end{etaremune}