\pdfbookmark[2]{International Conference Papers}{international-conference-papers}
\subsection*{International Conference Papers}
\label{publications:international-conference-papers}

\begin{etaremune}
    \item Théo Guyard, Cédric Herzet, Clément Elvira, and Ay\c{s}e-Nur Arslan. ``A new Branch-and-Bound pruning framework for L0-regularized problems''. \textit{In Forty-first International Conference on Machine Learning.} PMLR. 2024.
    \item Théo Guyard, Gilles Monnoyer, Cédric Herzet,  and Clément Elvira. ``Safe peeling for L0-regularized least-squares''. \textit{In European Conference on Signal Processing (EUSIPCO).} IEEE. 2023.
    \item Théo Guyard, Cédric Herzet, and Clément Elvira. ``Node-screening tests for L0-penalized least-squares problem''. \textit{In International Conference on Acoustics, Speech, and Signal Processing (ICASSP).} IEEE. 2022.
    \item Théo Guyard, Cédric Herzet, and Clément Elvira. ``Screen \& Relax: Accelerating the resolution of Elastic-net by safe identification of the solution support''. \textit{In International Conference on Acoustics, Speech, and Signal Processing (ICASSP).} IEEE. 2022.
\end{etaremune}

\pdfbookmark[2]{National Conference Papers}{national-conference-papers}
\subsection*{National Conference Papers}
\label{publications:national-conference-papers}

\begin{etaremune}
    \item Théo Guyard, Gilles Monnoyer, Cédric Herzet,  and Clément Elvira. ``Peeling pour le problème des moindres carrés avec régularisation L0''. \textit{In Groupe de Recherche et d'Etudes de Traitement du Signal et des Images (GRETSI).} 2023.
    \item Théo Guyard. ``An efficient solver for L0-penalized sparse problems''. \textit{In Congrès de la Société Française de Recherche Opérationnelle et d'Aide à la Décision (ROADEF).} 2023.
    \item Théo Guyard, Cédric Herzet, Clément Elvira, and Ay\c{s}e-Nur Arslan. ``Node-screening pour le problème des moindres carrés avec pénalité L0''. \textit{In Groupe de Recherche et d'Etudes de Traitement du Signal et des Images (GRETSI).} 2022.
    \item Théo Guyard, Cédric Herzet, and Clément Elvira. ``Screen \& Relax: Accélérer la résolution du problème "Elastic-Net" par identification du support de la solution''. \textit{In Groupe de Recherche et d'Etudes de Traitement du Signal et des Images (GRETSI).} 2022.
\end{etaremune}


\pdfbookmark[2]{Theses and Technical Reports}{theses-and-technical-reports}
\subsection*{Theses and Technical Reports}
\label{publications:theses-and-technical-reports}

\begin{etaremune}
    \item Théo Guyard. ``Branch-and-Bound algorithms for L0-regularized problems''. \textit{PhD thesis.} 2024.
    \item Théo Guyard. ``Acceleration methods for L0 and L1 regularized problems''. \textit{Engineering thesis.} 2021.
    \item Théo Guyard. ``Stochastic models for Kidney Exchange Programs''. \textit{Research program thesis.} 2020.
\end{etaremune}




% \pdfbookmark[2]{Working papers}{working-papers}
% \subsection*{Working papers}
% \label{working-papers}
% \newrefcontext[labelprefix=W]
% \printbibliography[type=misc,heading=none,resetnumbers=true,keyword=R]