The complete list of publications is available on my \href{https://github.com/TheoGuyard}{Github} profile.

\pdfbookmark[2]{Projects as Maintainer}{projects-as-maintainer}
\subsection*{Projects as Maintainer}
\label{tools:projects-as-maintainer}

\begin{longtable}[l]{@{}p{.125\textwidth}p{0.875\textwidth}}
    \href{https://github.com/TheoGuyard/ExpFlow/tree/main}{\texttt{exprun}} & Python toolbox to automatize pipelines for reproducible experiments. The package is available on \href{https://pypi.org/project/exprun/}{\texttt{pypi}} under MIT license.\\
    %
    \href{https://github.com/TheoGuyard/El0ps/tree/main}{\texttt{el0ps}} & Python toolbox to solve L0-regularized problems via flexible and numerically efficient methods. The package is available on \href{https://pypi.org/project/el0ps/}{\texttt{pypi}} under AGPL-v3 license. \\
    %
    \href{https://github.com/TheoGuyard/LIBSVMdata.jl}{\texttt{libsvmdata}} & Simple tool to fetch \href{https://www.csie.ntu.edu.tw/~cjlin/libsvmtools/datasets/}{LIBSVM} datasets to Julia. The package is available on \href{https://juliapackages.com/packages/libsvmdata}{\texttt{juliapackages}} under MIT license. \\
    %
    % \href{https://github.com/TheoGuyard/StochasticKEP.jl}{\texttt{StochasticKEP}} & Julia package to formulate Kidney Exchange Programs as stochastic optimization problems and solve them.
\end{longtable}

\pdfbookmark[2]{Projects as Contributor}{projects-as-contributor}
\subsection*{Projects as Contributor}
\label{tools:projects-as-contributor}

\begin{longtable}[l]{@{}p{.125\textwidth}p{0.875\textwidth}}
    \href{https://github.com/benchopt/benchopt}{\texttt{benchopt}} & BenchOpt is a benchmarking suite for optimization algorithms. It is built for simplicity, transparency, and reproducibility. The package is available on \href{https://pypi.org/project/benchopt/}{\texttt{pypi}} under BSD-3 license. \\
    %
    \href{https://github.com/hazimehh/L0Learn}{\texttt{l0learn}} & Efficient algorithms for L0-regularized learning. It is built for simplicity, transparency, and reproducibility. The package is available on \href{https://cran.r-project.org/web/packages/L0Learn/index.html}{CRAN} and \href{https://pypi.org/project/l0learn/}{\texttt{pypi}}. \\
    %
    \href{https://github.com/mathurinm/libsvmdata}{\texttt{libsvmdata}} & A python util to fetch datasets from the \href{https://www.csie.ntu.edu.tw/~cjlin/libsvmtools/datasets/}{LIBSVM} website. The package is available on \href{https://pypi.org/project/libsvmdata/}{\texttt{pypi}} under BSD-3 license. \\
\end{longtable}

% \paragraph{En tant que contributeur}

% \begin{itemize}[labelindent=\parindent,leftmargin=2.5cm]
%     \item[\href{https://github.com/benchopt/benchopt}{\texttt{benchopt}}] Ce package Python permet la mise en place de pipelines et de benchmarks pour comparer les performances de méthodes numériques sur des problèmes d'optimisation. Il est disponible sur \href{https://pypi.org/project/benchopt/}{\texttt{pipy}} sous licence BSD 3.
%     \item[\href{https://github.com/hazimehh/L0Learn}{\texttt{L0Learn}}] Ce package R et Python permet de résoudre de manière approchée des problèmes d'optimisation avec régularisation L0. Il est disponible sur \href{https://cran.r-project.org/web/packages/L0Learn/index.html}{CRAN} et \href{https://pypi.org/project/l0learn/}{\texttt{pipy}}.
%     \item[\href{https://github.com/mathurinm/libsvmdata}{\texttt{libsvmdata}}] Ce package Python permet de télécharger et formater simplement des jeux de données de machine learning depuis \href{https://www.csie.ntu.edu.tw/~cjlin/libsvmtools/datasets/}{LIBSVM}. Il est disponible sur \href{https://pypi.org/project/libsvmdata/}{\texttt{pypi}} sous licence BSD 3. 
% \end{itemize}

